
\begin{thebibliography}{1}



%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Alphabetical by last name!
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


\bibitem{delphi}
A. Abbadi, D. Agrawal, S. Das, A. Elmore, A. Pucher and X. Yan.
Characterizing Tenant Behavior for Placement and Crisis Mitigation in Multitenant DBMSs.
In SIGMOD, pages 517-528, 2013.


\bibitem{coldesign}
D. Abadi, P. Boncz, S. Harizopoulos, S. Idreos, and Samual Madden.
The Design and Implmentation of Modern Column-Oriented Database Systems.
In Foundations and Trends in Databases, Vol. 5. No. 3, 2012.


\bibitem{coloverview}
D. Abadi, P. Boncz, and S. Harizopoulos
Column-oriented Database Systems
In VLDB, 2009


\bibitem{compression}
D. J. Abadi, S. R. Madden, N. Hachem.
Integrating Compression and Execution in Column-Oriented Database Systems.
In SIGMOD, 2006.


\bibitem{howdiff}
D. J. Abadi, S. R. Madden, N. Hachem.
Column-Stores vs. Row-Stores: How Different Are They Really?
In SIGMOD, 2008.


\bibitem{materialization}
D. J. Abadi, D. S. Myers, D. J. DeWitt, and S. R. Madden.
Materialization Strategies in a Column-Oriented DBMS.
In ICDE, 2007.


\bibitem{dbvm}
A. Aboulnaga, U. Minhas, K. Salem, J. Yadav.
Database Systems on Virtual Machines: How Much do You Lose? 
In ICDE Workshops, pages 35-41, 2008.


\bibitem{dbaasazure}
T. Cabot and L. Pizette.
Database as a Service: A Marketplace Assessment.
Web Page, Jan. 2012.
http://www.mitre.org/sites/default/files/pdf/cloud\_database\_service\_dbaas.pdf


\bibitem{bigtable}
F. Chang, J. Dean, S. Ghemawat, W. C. Hsieh, D. A. Wallach, M. Burrows, T. Chandra, A. Fikes, and R. E. Gruber.
Bigtable: A Distributed Storage System for Structured Data
In OSDI, 2006.


\bibitem{dbaas}
V. Cheung.
DBaaS 101: What It Is and What to Expect.
Web page, March 2014.
http://www.geniedb.com/dbaas-101-what-it-is-and-what-to-expect/


\bibitem{relcloud}
C. Curino, E. Jones, R. Popa, N. Malviya, E. Wu, S. Madden, H. Balakrishnan, N. Zeldovich.
Relational Cloud: A Database-as-a-Service for the Cloud.
In CIDR, paper 33, 2011.


\bibitem{dynamo}
G. DeCandia, D. Hastorun, M. Jampani, G. Kakulapati, A. Lakshman, A. Pilchin, S. Sivasubramanian, P. Vosshall and W. Vogels.
Dynamo: Amazon's Highly Available Key-value Store.
SOSP, 2007.


\bibitem{sqlserver}
P. Larson, E. N. Hanson, and S. L. Price.
Columnar Storage in SQL Server 2012
In IEEE bullitin, 2012.


\bibitem{dbseer}
B. Mozafari, C. Curino and S. Madden.
DBSeer: Resource and Performance Prediction for Building a Next Generation Database Cloud.
In CIDR, paper 52, 2013.

\bibitem{cstore}
D. Abadi, P. Boncz, S. Harizopoulos, S. Idreos, and Samual Madden.
C-Store: A COlumn-Oriented DBMS
Web Page: http://db.csail.mit.edu/projects/cstore/


\bibitem{starschema}
P. O'Neil, B. O'Neil, X. Chen.
Star Schema Benchmark.
Web Page (Revision 3, 2009): http://www.cs.umb.edu/~poneil/StarSchemaB.PDF.


\bibitem{moore}
Intel.
Moore's Law: Raising the Bar.
2005.


\bibitem{vertica}
Vertica.
Vertica Crunchbase.
Web Page: http://www.crunchbase.com/company/vertica-systems.

\bibitem{calvin}
D. Abadi, T. Diamond, K. Ren, P. Shao, A. Thomson, and S. Weng.
Calvin: Fast Distributed Transactions for Partitioned Database Systems. 
In Proceedings of the ACM SIGMOD International Conference on Management of Data, page 1–12, 2012.

\bibitem{oltpbench}
P. Cudre-Mauroux, C. Curino, D. Difallah, and A. Pavlo.
OLTP-Bench: An Extensible Testbed for Benchmarking Relational Databases
In VLDB, 2014.

\bibitem{hyder}
P. Bernstein, C. Rein, and S. Das. 
Hyder – A Transactional Record Manager for Shared Flash. 
In CIDR, 2011.

\bibitem{vll}
D. Abadi, K. Ren, and A. Thomson.
Lightweight Locking for Main Memory Database Systems.
In PVLDB, vol. 6, no. 2, 2013.

\bibitem{horticulture}
C. Curino, A. Pavlo, and S. Zdonik.
Skew-Aware Automatic Database Partitioning in Shared-Nothing, Parallel OLTP Systems.
In ACM SIGMOD, 2012.





\end{thebibliography}


