
\subsection{Member Functions}

\subsubsection{\code{Stream<T>(T head, std::function<T>()> gen)}}

Default Stream constructor.
Takes an initial head value, and a function that returns a Stream.
The programmer should not have to interact with this method directly.
Instead, use the one of the four Stream creation helper functions, \code{from()}, \code{repeat()}, \code{iterate()}, or \code{recurrence()}.


\begin{lstlisting}[title=example]
std::function<Stream<int>()> ones = [&]() { return Stream<int>(1, ones) };
std::cout << ones().take(3) << std::endl;

// [1,1,1]
\end{lstlisting}

\subsubsection{\code{Stream<T>(T head, Stream<T> tail)}}

Tail-only Stream constructor.
The programmer should not have to interact with this method directly.

\subsubsection{\code{Stream<T>::head()}}

Return the first element of the Stream.

\begin{lstlisting}[title=example]
std::cout << from(1).head() << std::endl;

// 1
\end{lstlisting}

\subsubsection{\code{Stream<T>::tail()}}

Return the Stream minus the current head.

\begin{lstlisting}[title=example]
std::cout << from(1).tail().head() << std::endl;

// 2
\end{lstlisting}

\subsubsection{\code{Stream<T>::take(int n)}}

Return \code{n} elements taken from the Stream as a Collection.

\begin{lstlisting}[title=example]
std::cout << from(1).take(5) << std::endl;

// [1,2,3,4,5]
\end{lstlisting}

\subsubsection{\code{Stream<T>::filter(std::function<bool(T)> func)}}

Return a Stream that contains the elements of the initial Stream that match the predicate function.

\begin{lstlisting}[title=example]
auto evens = from(1).filter([](int x) { return x % 2 == 0; });
std::cout << evens.take(5) << std::endl;

// [2,4,6,8,10]
\end{lstlisting}

\subsubsection{\code{Stream<T>::map(Function func)}}

Return the Stream that results from the transformation of each element in the original Stream.

\begin{lstlisting}[title=example]
auto squares = from(1).map([](int x) { return x * x; });
std::cout << squares.take(5) << std::endl;

// [1,4,9,16,25]
\end{lstlisting}

\subsection{Non-member Functions}

\subsubsection{\code{cons(T value, Stream<T> other)}}

Prepends a value to a Stream.

\begin{lstlisting}[title=example]
auto ints = from(1);
std:cout << cons(10, ints).take(5) << std::endl;

// [10,1,2,3,4]
\end{lstlisting}

\subsubsection{\code{operator\&(T value, Stream<T> other)}}

Prepends a value to a Stream.

\begin{lstlisting}[title=example]
auto ints = from(1);
std:cout << (10 & (20 & ints)).take(5) << std::endl;

// [10,20,1,2,3]
\end{lstlisting}

\subsubsection{\code{repeate(T value)}}

Construct an infinite Stream of the given value.

\begin{lstlisting}[title=example]
std:cout << repeat(1).take(5) << std::endl;

// [1,1,1,1,1]
\end{lstlisting}


\subsubsection{\code{from(T n, T step=1)}}

Construct a Stream, starting at n, incrementing by step (defaults to 1).

\begin{lstlisting}[title=example]
std:cout << from(1).take(5) << std::endl;

// [1,2,3,4,5]
\end{lstlisting}

\subsubsection{\code{iterate(T value, Function func)}}

Construct an infinite Stream in terms of an initial value \code{x}, and a function \code{f}.
The Stream is then constructed as \code{x, f(x), f(f(x)), f(f(f(x)))...}.

\begin{lstlisting}[title=example]
std::cout <<  iterate(0, [](int x) { return x+1; }).take(5) << std::endl;

// [0,1,2,3,4]
\end{lstlisting}

\subsubsection{\code{recurrence(Function func, std::tuple<U...> args)}}

A generalized version of \code{iterate()}, which allows the user to define an infinite Stream in terms of any number of arguments, stored in a tuple, and a function that takes that tuple.

\begin{lstlisting}[title=example]
auto fibs = recurrence([](std::tuple<int,int> t) {
    return std::get<0>(t) + std::get<1>(t);
}, std::make_tuple(0, 1));
std::cout << fibs.take(5) << std::endl;

// [0,1,1,2,3]
\end{lstlisting}



\subsubsection{\code{zip(Stream<U>... other)}}

Return a Stream of tuples, where each tuple contains the elements of the zipped Streams that occur at the same position

\subsubsection{\code{zipWith(Function func, Stream<U>... other)}}

Generalizes zip by zipping with the function given as the first argument instead of a tupling function.



